Probabilistic Catalogs for Crowded Stellar Fields

### 2012-11-19 paper/ms.tex
Elaborate in abstract about sextractor failure

\begin{abstract}
We introduce a probabilistic (Bayesian) method for producing catalogs
from images of crowded stellar fields. The method is capable of handling the
challenges introduced by overlapping sources and is able to determine the luminosity
function of the stars even when the precise luminosity of each star is uncertain.
This is in contrast with standard techniques which produce a single catalog,
potentially underestimating the uncertainties in any study of the stellar
population. The method is implemented using advanced Markov Chain Monte Carlo
(MCMC) techniques including Reversible Jump and Nested Sampling.
The computational feasibility of the method is
demonstrated on simulated data where the luminosity function of the stars is a
broken power-law. The parameters of the luminosity function can be recovered
with moderate uncertainty. We compare the results obtained from our method
with those obtained from the \sex~software and find that the latter is
unable to correctly infer the number of stars or the parameters of the luminosity
function.
\end{abstract}

>>>>

\begin{abstract}
We introduce a probabilistic (Bayesian) method for producing catalogs
from images of crowded stellar fields. The method is capable of handling the
challenges introduced by overlapping sources and is able to determine the luminosity
function of the stars even when the precise luminosity of each star is uncertain.
This is in contrast with standard techniques which produce a single catalog,
potentially underestimating the uncertainties in any study of the stellar
population. The method is implemented using advanced Markov Chain Monte Carlo
(MCMC) techniques including Reversible Jump and Nested Sampling.
The computational feasibility of the method is
demonstrated on simulated data where the luminosity function of the stars is a
broken power-law. The parameters of the luminosity function can be recovered
with moderate uncertainties. We compare the results obtained from our method
with those obtained from the \sex~software and find that the latter significantly
underestimates the number of stars in the image and leads to incorrect
inferences about the luminosity function of the stars.
\end{abstract}
